si: code and prose exploring Spatial Interaction models

### 2022-04-15 README.qmd
Update docs, tests will pass!

```{r}
zones = get_pct_zones(region = "west-yorkshire", geography = "msoa")
centroids = get_pct_centroids(region = "west-yorkshire", geography = "msoa")
zones = zones %>% 
  filter(lad_name == "Leeds")
centroids = centroids %>% 
  filter(lad_name == "Leeds")
tm_shape(zones) + tm_polygons("all", palette = "viridis")
```

@@

```{r}
summary(od_df$fc)
od_df %>% 
  ggplot() +
  geom_point(aes(length, fc))
```

>>>>

```{r}
#| label: inputs
zones = get_pct_zones(region = "west-yorkshire", geography = "msoa")
centroids = get_pct_centroids(region = "west-yorkshire", geography = "msoa")
zones = zones %>% 
  filter(lad_name == "Leeds")
centroids = centroids %>% 
  filter(lad_name == "Leeds")
tm_shape(zones) + tm_polygons("all", palette = "viridis")
```

@@

```{r}
#| label: distance_decay
summary(od_df$fc)
od_df %>% 
  ggplot() +
  geom_point(aes(length, fc))
```
